---
output:
  html_document:
    keep_md: yes
    toc: no
    self_contained: no
---

## CSAT

#### Maintainer: *Marcus W. Beck, marcusb@sccwrp.org*

The California Stream Assessment Toolbox is a combined package for the [CSCI](https://github.com/SCCWRP/CSCI) (California Stream Condition Index), [ASCI](https://github.com/SCCWRP/ASCI) (Algal Stream Condition Index), and [PHAB](https://github.com/SCCWRP/PHAB) (Physical Habitat index) packages.  The functionality of each index is the same in CSAT as in the original packages.  This package exists solely as a convenience for installation. 

## Installation

Install the package as follows:

```{r, eval = FALSE}
install.packages('devtools')
library(devtools)
install_github('SCCWRP/CSAT')
library(CSAT)
```

## Usage

`library(CSAT)` will load the core CSAT packages:

* [CSCI](https://github.com/SCCWRP/CSCI), California Stream Condition Index. 
* [ASCI](https://github.com/SCCWRP/ASCI), Algal Stream Condition Index.
* [PHAB](https://github.com/SCCWRP/PHAB), for Physical Habitat index.

You will receive startup messages indicating the pacckages are being loaded:

```{r example}
library(CSAT)
```

### CSCI

```{r}
data(bugs_stations)
results <- CSCI(bugs = bugs_stations[[1]], stations = bugs_stations[[2]])
ls(results)
```

### ASCI

```{r}
data(demo_algae_tax)
data(demo_algae_sitedata)
demo_results <- ASCI(taxain = demo_algae_tax, sitein = demo_algae_sitedata)
demo_results
scores(demo_results)
```

### PHAB

```{r}
data(stations)
data(phab)
IPI(stations = stations, phab = phab)
```

## Updates

And you can check that all CSAT packages are up-to-date with `CSAT_update()`:

```{r update, eval = FALSE}
CSAT_update()
```

## Attribution

This package pillaged code from [tidyverse](https://github.com/tidyverse/tidyverse).

